---
title: "Netlogo_output_anaylsis"
author: "Veronika Juhasz"
date: "5/20/2021"
output: html_document
---

---
title: "Untitled"
author: "Veronika Juhasz"
date: "5/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(tidyverse, dplyr)

setwd("/Users/veronikajuhasz/Documents/University/Cognitive_science_AU/Semester_4/Soc_cult/exam/SocCult_ExamProj")

getwd()


```



to-dos:
- read in dataframes - DONE
- remove unneccessary rows (top section) - DONE
- leave only 1 ticks column, remove the rest - DONE
- rename column headers - DONE
- remove ticks over 2920 - DONE
- remove duplicates (keep every 10th row) - DONE
- make aggregate data per condition (sum the 10 trials per condition) - DONE
- compare conditions 

```{r}

data.preprocessing <- function(dat) {
  dat %>% 
  select(
     ticks = x,
     mean_opinion_global = y,
     var_opinion_global = y.1,
     sd_opinion_global = y.2,
     mean_opinion_group_1 = y.3,
     var_opinion_group_1 = y.4,
     sd_opinion_group_1 = y.5,
     mean_opinion_group_0 = y.6,
     var_opinion_group_0 = y.7,
     sd_opinion_group_0 = y.8,
     mean_opinion_group_neg1 = y.9,
     var_opinion_group_neg1 = y.10,
     sd_opinion_group_neg1= y.11, 
     mean_opinion_left = y.12,
     var_opinion_left= y.13,
     sd_opinion_left= y.14,
     mean_opinion_mid_left= y.15,
     var_opinion_mid_left = y.16,
     sd_opinion_mid_left = y.17,
     mean_opinion_middle = y.18,
     var_opinion_middle = y.19,
     sd_opinion_middle = y.20,
     mean_opinion_mid_right= y.21,
     var_opinion_mid_right= y.22,
     sd_opinion_mid_right= y.23,
     mean_opinion_right = y.24,
     var_opinion_right = y.25,
     sd_opinion_right = y.26,
     polarization_index = y.27,
     percent_extremists= y.28,
     percent_extremists_1= y.29,
     percent_extremists_neg1= y.30 ) %>% 
  filter(
      ticks < 2921,
      row_number() %% 10 == 1)
}


```


```{r}


cond1_trial1 <- read.csv("exam_data/Netlogo_output/Condition_1/1exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond1_trial1"
  )

cond1_trial2 <- read.csv("exam_data/Netlogo_output/Condition_1/2exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond1_trial2"
  )

cond1_trial3 <- read.csv("exam_data/Netlogo_output/Condition_1/3exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond1_trial3"
  )

cond1_trial4 <- read.csv("exam_data/Netlogo_output/Condition_1/4exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond1_trial4"
  )

cond1_trial5 <- read.csv("exam_data/Netlogo_output/Condition_1/5exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond1_trial5"
  )

cond1_trial6 <- read.csv("exam_data/Netlogo_output/Condition_1/6exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond1_trial6"
  )

cond1_trial7 <- read.csv("exam_data/Netlogo_output/Condition_1/7exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond1_trial7"
  )

cond1_trial8 <- read.csv("exam_data/Netlogo_output/Condition_1/8exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond1_trial8"
  )

cond1_trial9 <- read.csv("exam_data/Netlogo_output/Condition_1/9exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond1_trial9"
  )

cond1_trial10 <- read.csv("exam_data/Netlogo_output/Condition_1/10exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond1_trial10"
  )

cond1_combined <- rbind(cond1_trial1, cond1_trial2, cond1_trial3, cond1_trial4, cond1_trial5, cond1_trial6, cond1_trial7, cond1_trial8, cond1_trial9, cond1_trial10 )

summary_cond1_combined <- cond1_combined %>% 
  group_by(ticks) %>%
  summarise(
    mean_opinion_global = mean(mean_opinion_global),
    var_opinion_global = mean(var_opinion_global),
    sd_opinion_global = mean(sd_opinion_global),
    polarization_index = mean(polarization_index)) %>%
  mutate(condition = "Condition 1")
  
```


```{r}
cond2_trial1 <- read.csv("exam_data/Netlogo_output/Condition_2/1exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond2_trial1"
  )

cond2_trial2 <- read.csv("exam_data/Netlogo_output/Condition_2/2exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond2_trial2"
  )

cond2_trial3 <- read.csv("exam_data/Netlogo_output/Condition_2/3exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond2_trial3"
  )

cond2_trial4 <- read.csv("exam_data/Netlogo_output/Condition_2/4exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond2_trial4"
  )

cond2_trial5 <- read.csv("exam_data/Netlogo_output/Condition_2/5exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond2_trial5"
  )

cond2_trial6 <- read.csv("exam_data/Netlogo_output/Condition_2/6exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond2_trial6"
  )

cond2_trial7 <- read.csv("exam_data/Netlogo_output/Condition_2/7exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond2_trial7"
  )

cond2_trial8 <- read.csv("exam_data/Netlogo_output/Condition_2/8exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond2_trial8"
  )

cond2_trial9 <- read.csv("exam_data/Netlogo_output/Condition_2/9exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond2_trial9"
  )

cond2_trial10 <- read.csv("exam_data/Netlogo_output/Condition_2/10exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond2_trial10"
  )



cond2_combined <- rbind(cond2_trial1, cond2_trial2, cond2_trial3, cond2_trial4, cond2_trial5, cond2_trial6, cond2_trial7, cond2_trial8, cond2_trial9, cond2_trial10 )

summary_cond2_combined <- cond2_combined %>% 
  group_by(ticks) %>%
  summarise(
  mean_opinion_global = mean(mean_opinion_global),
  var_opinion_global = mean(var_opinion_global),
  sd_opinion_global = mean(sd_opinion_global),
  polarization_index = mean(polarization_index)
) %>%
  mutate(condition = "Condition 2")

```


```{r}
cond3_trial1 <- read.csv("exam_data/Netlogo_output/Condition_3/1exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond3_trial1"
  )

cond3_trial2 <- read.csv("exam_data/Netlogo_output/Condition_3/2exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond3_trial2"
  )

cond3_trial3 <- read.csv("exam_data/Netlogo_output/Condition_3/3exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond3_trial3"
  )

cond3_trial4 <- read.csv("exam_data/Netlogo_output/Condition_3/4exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond3_trial4"
  )

cond3_trial5 <- read.csv("exam_data/Netlogo_output/Condition_3/5exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond3_trial5"
  )

cond3_trial6 <- read.csv("exam_data/Netlogo_output/Condition_3/6exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond3_trial6"
  )

cond3_trial7 <- read.csv("exam_data/Netlogo_output/Condition_3/7exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond3_trial7"
  )

cond3_trial8 <- read.csv("exam_data/Netlogo_output/Condition_3/8exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond3_trial8"
  )

cond3_trial9 <- read.csv("exam_data/Netlogo_output/Condition_3/9exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond3_trial9"
  )

cond3_trial10 <- read.csv("exam_data/Netlogo_output/Condition_3/10exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond3_trial10"
  )


cond3_combined <- rbind(cond3_trial1, cond3_trial2, cond3_trial3, cond3_trial4, cond3_trial5, cond3_trial6, cond3_trial7, cond3_trial8, cond3_trial9, cond3_trial10 )

summary_cond3_combined <- cond3_combined %>% 
  group_by(ticks) %>%
  summarise(
  mean_opinion_global = mean(mean_opinion_global),
  var_opinion_global = mean(var_opinion_global),
  sd_opinion_global = mean(sd_opinion_global),
  polarization_index = mean(polarization_index)
) %>%
  mutate(condition = "Condition 3")



```


```{r}

cond4_trial1 <- read.csv("exam_data/Netlogo_output/Condition_4/1exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond4_trial1"
  )

cond4_trial2 <- read.csv("exam_data/Netlogo_output/Condition_4/2exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond4_trial2"
  )

cond4_trial3 <- read.csv("exam_data/Netlogo_output/Condition_4/3exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond4_trial3"
  )

cond4_trial4 <- read.csv("exam_data/Netlogo_output/Condition_4/4exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond4_trial4"
  )

cond4_trial5 <- read.csv("exam_data/Netlogo_output/Condition_4/5exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond4_trial5"
  )

cond4_trial6 <- read.csv("exam_data/Netlogo_output/Condition_4/6exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond4_trial6"
  )

cond4_trial7 <- read.csv("exam_data/Netlogo_output/Condition_4/7exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond4_trial7"
  )

cond4_trial8 <- read.csv("exam_data/Netlogo_output/Condition_4/8exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond4_trial8"
  )

cond4_trial9 <- read.csv("exam_data/Netlogo_output/Condition_4/9exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond4_trial9"
  )

cond4_trial10 <- read.csv("exam_data/Netlogo_output/Condition_4/10exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond4_trial10"
  )


cond4_combined <- rbind(cond4_trial1, cond4_trial2, cond4_trial3, cond4_trial4, cond4_trial5, cond4_trial6, cond4_trial7, cond4_trial8, cond4_trial9, cond4_trial10 )

summary_cond4_combined <- cond4_combined %>% 
  group_by(ticks) %>%
  summarise(
  mean_opinion_global = mean(mean_opinion_global),
  var_opinion_global = mean(var_opinion_global),
  sd_opinion_global = mean(sd_opinion_global),
  polarization_index = mean(polarization_index)
) %>%
  mutate(condition = "Condition 4")


```


```{r}
cond5_trial1 <- read.csv("exam_data/Netlogo_output/Condition_5/1exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond5_trial1"
  )

cond5_trial2 <- read.csv("exam_data/Netlogo_output/Condition_5/2exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond5_trial2"
  )

cond5_trial3 <- read.csv("exam_data/Netlogo_output/Condition_5/3exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond5_trial3"
  )

cond5_trial4 <- read.csv("exam_data/Netlogo_output/Condition_5/4exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond5_trial4"
  )

cond5_trial5 <- read.csv("exam_data/Netlogo_output/Condition_5/5exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond5_trial5"
  )

cond5_trial6 <- read.csv("exam_data/Netlogo_output/Condition_5/6exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond5_trial6"
  )

cond5_trial7 <- read.csv("exam_data/Netlogo_output/Condition_5/7exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond5_trial7"
  )

cond5_trial8 <- read.csv("exam_data/Netlogo_output/Condition_5/8exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond5_trial8"
  )

cond5_trial9 <- read.csv("exam_data/Netlogo_output/Condition_5/9exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond5_trial9"
  )

cond5_trial10 <- read.csv("exam_data/Netlogo_output/Condition_5/10exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond5_trial10"
  )



cond5_combined <- rbind(cond5_trial1, cond5_trial2, cond5_trial3, cond5_trial4, cond5_trial5, cond5_trial6, cond5_trial7, cond5_trial8, cond5_trial9, cond5_trial10 )

summary_cond5_combined <- cond5_combined %>% 
  group_by(ticks) %>%
  summarise(
  mean_opinion_global = mean(mean_opinion_global),
  var_opinion_global = mean(var_opinion_global),
  sd_opinion_global = mean(sd_opinion_global),
  polarization_index = mean(polarization_index)
) %>%
  mutate(condition = "Condition 5")


```


```{r}

cond6_trial1 <- read.csv("exam_data/Netlogo_output/Condition_6/1exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond6_trial1"
  )

cond6_trial2 <- read.csv("exam_data/Netlogo_output/Condition_6/2exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond6_trial2"
  )

cond6_trial3 <- read.csv("exam_data/Netlogo_output/Condition_6/3exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond6_trial3"
  )

cond6_trial4 <- read.csv("exam_data/Netlogo_output/Condition_6/4exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond6_trial4"
  )

cond6_trial5 <- read.csv("exam_data/Netlogo_output/Condition_6/5exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond6_trial5"
  )

cond6_trial6 <- read.csv("exam_data/Netlogo_output/Condition_6/6exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond6_trial6"
  )

cond6_trial7 <- read.csv("exam_data/Netlogo_output/Condition_6/7exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond6_trial7"
  )

cond6_trial8 <- read.csv("exam_data/Netlogo_output/Condition_6/8exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond6_trial8"
  )

cond6_trial9 <- read.csv("exam_data/Netlogo_output/Condition_6/9exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond6_trial9"
  )

cond6_trial10 <- read.csv("exam_data/Netlogo_output/Condition_6/10exam_v13_groupbyopinion_movebycolor - cleared - fixed - FINAL Super combined plot.csv", skip = 46, header = T) %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond6_trial10"
  )


cond6_combined <- rbind(cond6_trial1, cond6_trial2, cond6_trial3, cond6_trial4, cond6_trial5, cond6_trial6, cond6_trial7, cond6_trial8, cond6_trial9, cond6_trial10 )

summary_cond6_combined <- cond6_combined %>% 
  group_by(ticks) %>%
  summarise(
  mean_opinion_global = mean(mean_opinion_global),
  var_opinion_global = mean(var_opinion_global),
  sd_opinion_global = mean(sd_opinion_global),
  polarization_index = mean(polarization_index)
) %>%
  mutate(condition = "Condition 6")


```





```{r}
## Hypothesis 1: comapring Condition 1 and condition 2

## Condition 1

cond1_combined %>% 
  ggplot(aes(x = ticks, y = mean_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean opinion of the different trials in Condition 1")

cond1_combined %>% 
  ggplot(aes(x = ticks, y = var_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Variance of opinion of the different trials in Condition 1")


cond1_combined %>% 
  ggplot(aes(x = ticks, y = sd_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs ( title = "Standard deviation of opinion of the different trials in Condition 1")


cond1_combined %>% 
  ggplot(aes(x = ticks, y = polarization_index, color = condition)) +
  geom_point(size = 0.5) +
  labs ( title = "Polarization index of the different trials in Condition 1")


## Condition 1

cond2_combined %>% 
  ggplot(aes(x = ticks, y = mean_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs ( title = "Mean opinion of the different trials in Condition 2")

cond2_combined %>% 
  ggplot(aes(x = ticks, y = var_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Variance of opinion of the different trials in Condition 2")


cond2_combined %>% 
  ggplot(aes(x = ticks, y = sd_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Standard deviation of opinion of the different trials in Condition 2")


cond2_combined %>% 
  ggplot(aes(x = ticks, y = polarization_index, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Polarization index of the different trials in Condition 2")





summary_cond1_cond2 <- rbind(summary_cond1_combined, summary_cond2_combined)

summary_cond1_cond2 %>% 
  ggplot(aes(x = ticks, y = mean_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean opinion of the different conditions")

summary_cond1_cond2 %>% 
  ggplot(aes(x = ticks, y = var_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean Variance of opinion of the different conditions")


summary_cond1_cond2 %>% 
  ggplot(aes(x = ticks, y = sd_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean Standard dev. of opinion of the different conditions")


summary_cond1_cond2 %>% 
  ggplot(aes(x = ticks, y = polarization_index, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean polarization index of the different conditions")

```


```{r}
## Hypothesis 2: comapring Condition 3 and condition 4

## Condition 3

cond3_combined %>% 
  ggplot(aes(x = ticks, y = mean_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean opinion of the different trials in Condition 3")

cond3_combined %>% 
  ggplot(aes(x = ticks, y = var_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Variance of opinion of the different trials in Condition 3")


cond3_combined %>% 
  ggplot(aes(x = ticks, y = sd_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs ( title = "Standard deviation of opinion of the different trials in Condition 3")


cond3_combined %>% 
  ggplot(aes(x = ticks, y = polarization_index, color = condition)) +
  geom_point(size = 0.5) +
  labs ( title = "Polarization index of the different trials in Condition 3")


## Condition 4

cond4_combined %>% 
  ggplot(aes(x = ticks, y = mean_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs ( title = "Mean opinion of the different trials in Condition 4")

cond4_combined %>% 
  ggplot(aes(x = ticks, y = var_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Variance of opinion of the different trials in Condition 4")


cond4_combined %>% 
  ggplot(aes(x = ticks, y = sd_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Standard deviation of opinion of the different trials in Condition 4")


cond4_combined %>% 
  ggplot(aes(x = ticks, y = polarization_index, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Polarization index of the different trials in Condition 4")





summary_cond3_cond4 <- rbind(summary_cond3_combined, summary_cond4_combined)

summary_cond3_cond4 %>% 
  ggplot(aes(x = ticks, y = mean_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean opinion of the different conditions")

summary_cond3_cond4 %>% 
  ggplot(aes(x = ticks, y = var_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean Variance of opinion of the different conditions")


summary_cond3_cond4 %>% 
  ggplot(aes(x = ticks, y = sd_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean Standard dev. of opinion of the different conditions")


summary_cond3_cond4 %>% 
  ggplot(aes(x = ticks, y = polarization_index, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean polarization index of the different conditions")
```


```{r}
## Condition 5

cond5_combined %>% 
  ggplot(aes(x = ticks, y = mean_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean opinion of the different trials in Condition 5")

cond5_combined %>% 
  ggplot(aes(x = ticks, y = var_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Variance of opinion of the different trials in Condition 5")


cond5_combined %>% 
  ggplot(aes(x = ticks, y = sd_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs ( title = "Standard deviation of opinion of the different trials in Condition 5")


cond5_combined %>% 
  ggplot(aes(x = ticks, y = polarization_index, color = condition)) +
  geom_point(size = 0.5) +
  labs ( title = "Polarization index of the different trials in Condition 5")


## Condition 6

cond6_combined %>% 
  ggplot(aes(x = ticks, y = mean_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs ( title = "Mean opinion of the different trials in Condition 6")

cond6_combined %>% 
  ggplot(aes(x = ticks, y = var_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Variance of opinion of the different trials in Condition 6")


cond6_combined %>% 
  ggplot(aes(x = ticks, y = sd_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Standard deviation of opinion of the different trials in Condition 6")


cond6_combined %>% 
  ggplot(aes(x = ticks, y = polarization_index, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Polarization index of the different trials in Condition 6")





summary_cond5_cond6 <- rbind(summary_cond5_combined, summary_cond6_combined)

summary_cond5_cond6 %>% 
  ggplot(aes(x = ticks, y = mean_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean opinion of the different conditions")

summary_cond5_cond6 %>% 
  ggplot(aes(x = ticks, y = var_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean Variance of opinion of the different conditions")


summary_cond5_cond6 %>% 
  ggplot(aes(x = ticks, y = sd_opinion_global, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean Standard dev. of opinion of the different conditions")


summary_cond5_cond6 %>% 
  ggplot(aes(x = ticks, y = polarization_index, color = condition)) +
  geom_point(size = 0.5) +
  labs (title = "Mean polarization index of the different conditions")
```



