---
title: "Netlogo_output_anaylsis"
author: "Veronika Juhasz"
date: "5/20/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(tidyverse, dplyr, pastecs, WRS2, gridExtra)
library("ggpubr")

getwd()

```



```{r}


data.preprocessing <- function(dat) {
  dat %>% 
  select(
     ticks = x,
     mean_opinion_global = y,
     var_opinion_global = y.1,
     sd_opinion_global = y.2,
     polarization_index = y.27,
     percent_extremists= y.28,
     percent_extremists_1= y.29,
     percent_extremists_neg1= y.30,
     file_id) %>% 
  filter(
      ticks < 2921,
      ticks %% 10 == 0) %>% 
  mutate(
    trial = str_extract(file_id, "[^_]+$"),
    trial = str_extract(trial, ".*(?=\\.csv)")
  )
}

```



Reading in and transforming data for each condition:

```{r}

### Condition 1

files_cond1 <- list.files("./exam_data/Netlogo_output", pattern = "^exam_v15 Super combined plot_cond1.*?\\.csv", full.names = TRUE, recursive = T)

df_cond1 <- purrr::map_df(files_cond1, function(x) {
	data <- read.csv(x, skip = 46, header=TRUE)
	cbind(file_id = x, data)
	})

df_preprocessed_cond1 <- df_cond1 %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond1",
    Condition = "Low Gini"
  )


### Condition 2

files_cond2 <- list.files("./exam_data/Netlogo_output", pattern = "^exam_v15 Super combined plot_cond2.*?\\.csv", full.names = TRUE, recursive = T)

df_cond2 <- purrr::map_df(files_cond2, function(x) {
	data <- read.csv(x, skip = 46, header=TRUE)
	cbind(file_id = x, data)
	})

df_preprocessed_cond2 <- df_cond2 %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond2",
    Condition = "High Gini"
  )


### Condition 3

files_cond3 <- list.files("./exam_data/Netlogo_output", pattern = "^exam_v15 Super combined plot_cond3.*?\\.csv", full.names = TRUE, recursive = T)

df_cond3 <- purrr::map_df(files_cond3, function(x) {
	data <- read.csv(x, skip = 46, header=TRUE)
	cbind(file_id = x, data)
	})

df_preprocessed_cond3 <- df_cond3 %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond3",
    Condition = "High cooperation"
  )


### Condition 4

files_cond4 <- list.files("./exam_data/Netlogo_output", pattern = "^exam_v15 Super combined plot_cond4.*?\\.csv", full.names = TRUE, recursive = T)

df_cond4 <- purrr::map_df(files_cond4, function(x) {
	data <- read.csv(x, skip = 46, header=TRUE)
	cbind(file_id = x, data)
	})

df_preprocessed_cond4 <- df_cond4 %>% 
  data.preprocessing() %>% 
  mutate(
    condition = "cond4",
    Condition = "Low cooperation"
  )


```


Creating combined, filetered dataframes for the 2 hypotheses

```{r}

cond1_filtered <- df_preprocessed_cond1 %>% 
  filter(
    ticks > 2919
  )

cond2_filtered <- df_preprocessed_cond2 %>% 
  filter(
    ticks > 2919
  )

cond1_cond2_combined <- rbind(cond1_filtered, cond2_filtered)


cond3_filtered <- df_preprocessed_cond3 %>% 
  filter(
    ticks > 2919
  )

cond4_filtered <- df_preprocessed_cond4 %>% 
  filter(
    ticks > 2919
  )

cond3_cond4_combined <- rbind(cond3_filtered, cond4_filtered)
```



HYPOTHESIS 1: Societies with lower inequality of income will polarize at a slower rate than societies with higher inequality of income.
--> Condition 1 and 2 of the data


Checking t.test assumptions:

```{r}

############ Checking Assumptions for Condition 1 and Condition 2

p1 <- ggplot(cond1_cond2_combined, aes(polarization_index)) +
        geom_histogram(fill = "white", color = "grey30") +
        facet_wrap(~ condition)
p1


p2 <- ggplot(cond1_cond2_combined, aes(sample = polarization_index)) +
        stat_qq() +
        stat_qq_line(colour = 'red') +
        facet_wrap(~ condition)
p2


grid.arrange(p1, p2, nrow = 2)


shapiro.test(cond1_filtered$polarization_index) # normal distribution
shapiro.test(cond2_filtered$polarization_index) # normal distribution

#stat.desc
round(pastecs::stat.desc(cbind(cond1_filtered$polarization_index, cond2_filtered$polarization_index), basic = FALSE, norm = TRUE), digits = 2)

```

The qqplots and the Shapiro tests show a normal distribution.


Running t.test:

```{r}
t.test(polarization_index ~ condition, data = cond1_cond2_combined)

```


Report: Using an independent t-test, we found that the polarization index of condition 2 (M=0.25, SD=0.23) was significantly lower than the polarization index of condition 1 (M=0.44, SD=0.32), t(25.62)=2.101, p=0.046. 



Visualizing outcomes

```{r}
cond1_cond2_combined$condition <- as.factor(cond1_cond2_combined$condition)

ggplot(cond1_cond2_combined, aes(x = condition, y = polarization_index, colour = condition)) +
  theme_minimal() +
  labs(x = "Condition", y = "Polarization index") +
  geom_boxplot(width = 0.5) +
  ggtitle("Box Plot: polarization index depending on condition")



ggplot(cond1_cond2_combined, aes(x= Condition, y = polarization_index, fill = Condition)) +
  stat_summary(fun.y = mean,
               geom = "bar",
               width = 0.6) +
  stat_summary(fun.data = mean_se,
               geom = "errorbar",
               width = 0.2) +
  labs(x = "Condition", y = "Mean Polarization Index", title = "Mean Polarization Index with SE Error Bars" ) +
  theme_minimal()

```







HYPOTHESIS 2: More cooperative societies will polarize at a slower rate than less cooperative societies.

--> Condition 3 and condition 4 of the data.

```{r}

############ Checking Assumptions for Condition 3 and Condition 4


p3 <- ggplot(cond3_cond4_combined, aes(polarization_index)) +
        geom_histogram(fill = "white", color = "grey30") +
        facet_wrap(~ condition)
p3


p4 <- ggplot(cond3_cond4_combined, aes(sample = polarization_index)) +
        stat_qq() +
        stat_qq_line(colour = 'red') +
        facet_wrap(~ condition)
p4


grid.arrange(p3, p4, nrow = 2)


shapiro.test(cond3_filtered$polarization_index) # normal distribution
shapiro.test(cond4_filtered$polarization_index) # normal distribution


#stat.desc
round(pastecs::stat.desc(cbind(cond3_filtered$polarization_index, cond4_filtered$polarization_index), basic = FALSE, norm = TRUE), digits = 2)

```


Running the t.test:

```{r}
t.test(polarization_index ~ condition, data = cond3_cond4_combined)

```

Report: Using an independent t-test, we found that there was no significant difference in the polarization index of condition 3 (M=0.24, SD=0.26) and condition 4(M=0.34, SD=0.32), t(26.554)=-1.1249, p=0.2707. 


Visualizing outcomes:

```{r}

cond3_cond4_combined$condition <- as.factor(cond3_cond4_combined$condition)

ggplot(cond3_cond4_combined, aes(x = condition, y = polarization_index, colour = condition)) +
  theme_minimal() +
  labs(x = "Condition", y = "Polarization index") +
  geom_boxplot(width = 0.5) +
  ggtitle("Box Plot: polarization index depending on condition")



ggplot(cond3_cond4_combined, aes(x= Condition, y = polarization_index, fill = Condition)) +
  stat_summary(fun.y = mean,
               geom = "bar",
               width = 0.6) +
  stat_summary(fun.data = mean_se,
               geom = "errorbar",
               width = 0.2) +
  labs(x = "Condition", y = "Mean Polarization Index", title = "Mean Polarization Index with SE Error Bars" )+
  theme_minimal()


```